Make manuscript figures

### 2022-06-13 scripts/R/make_manuscript_figures.rmd
update simulation fig to have other 2 example points

# Get example simulation POUMM values to annotate plot with
example_data1 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75), estimate = 0.15),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60), estimate = 0.1))
example_data1$inference.method <- factor(
        example_data1$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))
example_data2 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85), estimate = 0.75),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60), estimate = 0.1))
example_data2$inference.method <- factor(
        example_data2$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))

@@

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("Heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black", aes(shape = "spVL")) + 
        geom_point(data = qdr_data, fill = "black", aes(shape = "QDR")) + 
        geom_point(data = example_data1, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data2, fill = "black", aes(shape = "Example")) +
        scale_shape_manual(values = c("QDR" = 16, "spVL" = 4, "Example" = 1), name = element_blank())

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("Heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black", aes(shape = "spVL")) + 
        geom_point(data = qdr_data, fill = "black", aes(shape = "QDR")) + 
        geom_point(data = example_data1, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data2, fill = "black", aes(shape = "Example")) +
        scale_shape_manual(values = c("QDR" = 16, "spVL" = 4, "Example" = 1), name = element_blank())

@@

Estimated trait values Xanthomonas
```{r}
p1 <- ggplot(data = traits_arboricola, aes(x = trait, y = h.MWA)) +
      geom_point() +
      shared_theme +
      labs(x = "Calculated QDR trait", y = ehat_name)
p2 <- ggExtra::ggMarginal(p1, type="histogram")
ggsave(plot = p2, filename = paste(FIGDIR, "trait_values_arboricola.png", sep = "/"),
      width = linewidth * 2/3, height = height * 2/3, units = "cm")
```

>>>>

# Get example simulation POUMM values to annotate plot with
example_data1 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75), estimate = 0.15),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60), estimate = 0.1))
example_data1$inference.method <- factor(
        example_data1$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))
example_data2 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85), estimate = 0.75),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60), estimate = 0.1))
example_data2$inference.method <- factor(
        example_data2$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))
example_data3 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85), estimate = 0.15),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60, 70), estimate = 60))
example_data3$inference.method <- factor(
        example_data3$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))
example_data4 <- data.frame(
        inference.method = "h.MWA.p.value",
        H2 = get_xval_for_sim_plots(real_vals = c(0.15, 0.25, 0.35, 0.45, 0.55, 0.65, 0.75, 0.85), estimate = 0.75),
        alpha = get_xval_for_sim_plots(real_vals = c(0.1, 0.5, 1, 5, 10, 20, 30, 40, 50, 60, 70), estimate = 60))
example_data4$inference.method <- factor(
        example_data4$inference.method,
        levels = c("h.plus.e.p.value", "h.MWA.p.value", "norm.z.p.value"),
        labels = c(e_name, ehat_name, z_minus_zbar_name))

@@

# Plot RMSE
rmse_plot <- plotHeatmap(
        df = data.summary,
        N.sim = data.summary$N.reps[[1]],
        is.MLE = T,
        scale.limits = c(0, 1),
        legend.name = "RMSE",
        midpoint = 0.5,
        fill.hi = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[1],
        fill.lo = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[3],
        fill.mid = RColorBrewer::brewer.pal(name = 'PiYG', n = 3)[2],
        x.var = "alpha",
        y.var = "H2",
        fill.var = "mean.error",
        facet.x = "inference.method",
        facet.y = NA,
        is.oob.squish = F,
        is.real.scale = F,
        labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("Heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black", aes(shape = "spVL")) + 
        geom_point(data = qdr_data, fill = "black", aes(shape = "QDR")) + 
        geom_point(data = example_data1, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data2, fill = "black", aes(shape = "Example")) +
        geom_point(data = example_data3, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data4, fill = "black", aes(shape = "Example")) +
        scale_shape_manual(values = c("QDR" = 16, "spVL" = 4, "Example" = 1), name = element_blank())

@@

# Plot TPR
tpr_plot <- makeTPRPlot(
        df = data.summary %>% filter(inference.method %in% c(e_name, ehat_name, z_minus_zbar_name)),
        is.MLE = T,
        midpoint = 0.5,
        fill.lo = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[3],
        fill.hi = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[1],
        fill.mid = RColorBrewer::brewer.pal(name = 'RdBu', n = 3)[2]) +
        facet_grid(. ~ inference.method, labeller = label_wrap_gen(width = 25)) +
        labs(x = expression("Selection strength (" * alpha * ")"),
             y = expression("Heritability (" * italic('H'^2) * ")")) +
        shared_theme +
        theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
        geom_point(data = spvl_data, fill = "black", aes(shape = "spVL")) + 
        geom_point(data = qdr_data, fill = "black", aes(shape = "QDR")) + 
        geom_point(data = example_data1, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data2, fill = "black", aes(shape = "Example")) +
        geom_point(data = example_data3, fill = "black", aes(shape = "Example")) + 
        geom_point(data = example_data4, fill = "black", aes(shape = "Example")) +
        scale_shape_manual(values = c("QDR" = 16, "spVL" = 4, "Example" = 1), name = element_blank())

@@

Estimated trait values Xanthomonas
```{r}
p1 <- ggplot(data = traits_arboricola, aes(x = trait, y = h.MWA)) +
      geom_point() +
      shared_theme +
      labs(x = "Calculated QDR trait", y = ehat_name)
p2 <- ggExtra::ggMarginal(p1, type="histogram")
ggsave(plot = p2, filename = paste(FIGDIR, "trait_values_arboricola.png", sep = "/"),
      width = linewidth * 2/3, height = height * 2/3, units = "cm")
```
Compare variance-covariance matrix under POUMM
```{r}
# Get variance-covariance matrix from POUMM
corr_HIV <- POUMM::covVTipsGivenTreePOUMM(
        tree = tree, 
        alpha = poumm_parameter_estimates[[which(poumm_parameter_estimates$stat == 'alpha'), 'PostMean']], 
        sigma = poumm_parameter_estimates[[which(poumm_parameter_estimates$stat == 'sigma'), 'PostMean']], 
        sigmae = poumm_parameter_estimates[[which(poumm_parameter_estimates$stat == 'sigmae'), 'PostMean']],
        corr = T
)
corr_arboricola <- POUMM::covVTipsGivenTreePOUMM(
        tree = tree_arboricola, 
        alpha = poumm_parameter_estimates_arboricola[[which(poumm_parameter_estimates_arboricola$stat == 'alpha'), 'PostMean']], 
        sigma = poumm_parameter_estimates_arboricola[[which(poumm_parameter_estimates_arboricola$stat == 'sigma'), 'PostMean']], 
        sigmae = poumm_parameter_estimates_arboricola[[which(poumm_parameter_estimates_arboricola$stat == 'sigmae'), 'PostMean']],
        corr = T
)
max(corr_HIV[upper.tri(corr_HIV)])
min(corr_HIV[upper.tri(corr_HIV)])
max(corr_arboricola[upper.tri(corr_arboricola)])
min(corr_arboricola[upper.tri(corr_arboricola)])
```
